---
title: "Advanced Usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Advanced Usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", eval = FALSE)
```

## Custom Headers

Pass a named character vector (or a named list of strings) to set custom
HTTP headers on the client (applied to every request):

```{r}
library(koon)

client <- Koon$new(
  "chrome",
  headers = c(
    "X-Custom-Header" = "my-value",
    "Accept-Language" = "de-DE,de;q=0.9"
  )
)

resp <- client$get("https://httpbin.org/headers")
cat(resp$text)
```

A header the browser profile already sends, like `Accept-Language` above,
keeps its browser position with your value; new headers are added in the
order given. `list("Accept-Language" = "de-DE")` works as well.

### Per-Request Headers

You can also set headers for a single request via the `headers` parameter.
Per-request headers override constructor-level headers (case-insensitive):

```{r}
# These headers apply only to this request
resp <- client$get("https://httpbin.org/headers",
  headers = c(Authorization = "Bearer my-token"))

# POST with per-request headers
resp <- client$post("https://httpbin.org/post", "data",
  headers = c("Content-Type" = "text/plain"))
```

## Choosing the Platform

Profile names without an OS impersonate Windows, the most common desktop
platform (Safari: macOS). Add an OS suffix to impersonate another platform:

```{r}
Koon$new("chrome-macos")$user_agent()
Koon$new("firefox-linux")$user_agent()
```

## Proxy Configuration

Route requests through an HTTP, HTTPS or SOCKS5 proxy:

```{r}
# HTTP proxy
client <- Koon$new("chrome", proxy = "http://proxy.example.com:8080")

# HTTPS proxy: TLS to the proxy, whose certificate is verified. For a proxy
# with a self-signed certificate or one from a private CA, trust that
# certificate (origins are still verified against the built-in roots)
client <- Koon$new("chrome", proxy = "https://proxy.example.com:443",
  proxy_ca_certs = readLines("proxy-ca.pem"))

# SOCKS5 proxy
client <- Koon$new("chrome", proxy = "socks5://127.0.0.1:1080")

# Proxy with authentication
client <- Koon$new("chrome", proxy = "http://user:pass@proxy.example.com:8080")

# Rotate through several proxies, one per request
client <- Koon$new("chrome",
  proxies = c("http://proxy1.example.com:8080", "http://proxy2.example.com:8080"))

resp <- client$get("https://httpbin.org/ip")
cat(resp$text)
```

## Timeout Configuration

Set the request timeout in seconds, fractions allowed (default: 30; `0`
means no timeout). A per-request `timeout` overrides the client's:

```{r}
# 10 second timeout
client <- Koon$new("chrome", timeout = 10)

# 2.5 seconds for a fast API
fast <- Koon$new("chrome", timeout = 2.5)

# 60 seconds for one slow endpoint
resp <- client$get("https://httpbin.org/delay/30", timeout = 60)
```

## Error Handling

koon raises errors on network failures, timeouts and invalid input. Every
error has the classes `koon_<code>`, `koon_error` and `error`, and its
`code` field holds the error code:

```{r}
client <- Koon$new("chrome", timeout = 5)

result <- tryCatch(
  client$get("https://httpbin.org/delay/10"),
  koon_timeout = function(e) {
    message("Timed out: ", conditionMessage(e))
    NULL
  },
  koon_error = function(e) {
    message("Request failed with ", e$code, ": ", conditionMessage(e))
    NULL
  }
)

if (!is.null(result) && result$ok) {
  cat("Status:", result$status, "\n")
}
```

Common codes are `TIMEOUT`, `CONNECTION_FAILED`, `TLS_ERROR`, `PROXY_ERROR`,
`INVALID_URL`, `TOO_MANY_REDIRECTS` and `INVALID_ARGUMENT`.

A helper function for retries. It catches only koon errors, so a mistake in
your own code still surfaces, and Ctrl-C / Esc still stops the loop: an
interrupt is not an error.

```{r}
request_with_retry <- function(client, url, max_retries = 3) {
  for (i in seq_len(max_retries)) {
    result <- tryCatch(client$get(url), koon_error = function(e) NULL)
    if (!is.null(result) && result$ok) return(result)
    Sys.sleep(2^i)  # exponential backoff
  }
  stop("Request failed after ", max_retries, " retries")
}

client <- Koon$new("chrome")
resp <- request_with_retry(client, "https://httpbin.org/get")
```

For transport errors koon can also retry by itself: `Koon$new(retries = 3)`.

## Redirect Callbacks

`on_request`, `on_response` and `on_redirect` let you watch or steer every
hop of a request. `on_redirect` returns `FALSE` to stop and get the 3xx
response; any other value, `NULL` from a logging function included,
follows the redirect:

```{r}
client <- Koon$new("chrome",
  on_response = function(status, url, headers) message(status, " ", url),
  on_redirect = function(status, url, headers) !grepl("captcha", url)
)
resp <- client$get("https://httpbin.org/redirect/3")
```

The same arguments on a request apply to that request only, in place of
the client's:

```{r}
resp <- client$get("https://httpbin.org/redirect/3",
  on_redirect = function(status, url, headers) FALSE)
resp$status  # 302
```

An error raised in a callback fails the request and reaches your code
unchanged, as the same condition. A failing `on_request` stops the request
before it is sent, so it can guard where requests go:

```{r}
guarded <- Koon$new("chrome", on_request = function(method, url) {
  if (!startsWith(url, "https://httpbin.org/")) stop("blocked: ", url)
})
tryCatch(guarded$get("https://httpbin.org/redirect-to?url=https://example.com/"),
  error = function(e) conditionMessage(e))
```

## Connecting to a Given Address

`resolve` takes entries in curl's `--resolve` format,
`"host:port:address"`: requests to that host and port connect to the
address instead of looking up the host. The TLS server name, the Host
header and the cookies stay those of the host, e.g. to test a server
before its DNS points to it:

```{r}
client <- Koon$new("chrome", resolve = "example.com:443:93.184.215.14")
```

## Closing Connections

`$close()` closes the pooled connections without waiting; the client stays
usable. Before the R session ends, `$shutdown()` ends them as a browser
does when it quits: every HTTP/3 connection closes at once, and the call
returns once the closes have been sent (at most 300 ms).

## Working with Response Headers

Response headers are returned as a data.frame, making them easy to filter:

```{r}
resp <- client$get("https://httpbin.org/response-headers?X-Test=hello")

# All headers
resp$headers

# Find a specific header
resp$headers[resp$headers$name == "x-test", "value"]

# Content-Type
resp$content_type
```

## Combining Options

All constructor parameters can be combined:

```{r}
client <- Koon$new(
  "firefox",
  proxy = "socks5://127.0.0.1:1080",
  timeout = 15,
  headers = c("Accept-Language" = "en-US,en;q=0.9")
)

resp <- client$get("https://httpbin.org/get")
```
