---
title: "Advanced Usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Advanced Usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", eval = FALSE)
```

## Custom Headers

Pass a named character vector to set custom HTTP headers on the client (applied to every request):

```{r}
library(koon)

client <- Koon$new(
  "chrome145",
  headers = c(
    "X-Custom-Header" = "my-value",
    "Accept-Language" = "de-DE,de;q=0.9"
  )
)

resp <- client$get("https://httpbin.org/headers")
cat(resp$text)
```

### Per-Request Headers

You can also set headers for a single request via the `headers` parameter.
Per-request headers override constructor-level headers (case-insensitive):

```{r}
# These headers apply only to this request
resp <- client$get("https://httpbin.org/headers",
  headers = c(Authorization = "Bearer my-token"))

# POST with per-request headers
resp <- client$post("https://httpbin.org/post", charToRaw("data"),
  headers = c("Content-Type" = "text/plain"))
```

## Fingerprint Randomization

Enable slight randomization of the browser fingerprint to avoid identical fingerprints across requests. This varies User-Agent build numbers, Accept-Language q-values, and HTTP/2 window sizes:

```{r}
client <- Koon$new("chrome145", randomize = TRUE)
cat(client$export_profile())  # slightly different each time
```

## Proxy Configuration

Route requests through an HTTP or SOCKS5 proxy:

```{r}
# HTTP proxy
client <- Koon$new("chrome145", proxy = "http://proxy.example.com:8080")

# SOCKS5 proxy
client <- Koon$new("chrome145", proxy = "socks5://127.0.0.1:1080")

# Proxy with authentication
client <- Koon$new("chrome145", proxy = "http://user:pass@proxy.example.com:8080")

resp <- client$get("https://httpbin.org/ip")
cat(resp$text)
```

## Timeout Configuration

Set a custom request timeout in milliseconds (default: 30000ms):

```{r}
# 10 second timeout
client <- Koon$new("chrome145", timeout = 10000)

# 60 second timeout for slow endpoints
client <- Koon$new("chrome145", timeout = 60000)
```

## Error Handling

koon raises errors on network failures, timeouts, and invalid responses. Use `tryCatch` to handle them:

```{r}
client <- Koon$new("chrome145", timeout = 5000)

result <- tryCatch(
  client$get("https://httpbin.org/delay/10"),
  error = function(e) {
    message("Request failed: ", conditionMessage(e))
    NULL
  }
)

if (!is.null(result) && result$ok) {
  cat("Status:", result$status, "\n")
}
```

A helper function for retries:

```{r}
request_with_retry <- function(client, url, max_retries = 3) {
  for (i in seq_len(max_retries)) {
    result <- tryCatch(client$get(url), error = function(e) NULL)
    if (!is.null(result) && result$ok) return(result)
    Sys.sleep(2^i)  # exponential backoff
  }
  stop("Request failed after ", max_retries, " retries")
}

client <- Koon$new("chrome145")
resp <- request_with_retry(client, "https://httpbin.org/get")
```

## Working with Response Headers

Response headers are returned as a data.frame, making them easy to filter:

```{r}
resp <- client$get("https://httpbin.org/response-headers?X-Test=hello")

# All headers
resp$headers

# Find a specific header
resp$headers[resp$headers$name == "x-test", "value"]

# Content-Type
ct <- resp$headers[resp$headers$name == "content-type", "value"]
cat("Content-Type:", ct, "\n")
```

## Combining Options

All constructor parameters can be combined:

```{r}
client <- Koon$new(
  "firefox147",
  proxy = "socks5://127.0.0.1:1080",
  timeout = 15000,
  randomize = TRUE,
  headers = c("Accept-Language" = "en-US,en;q=0.9")
)

resp <- client$get("https://httpbin.org/get")
```
