---
title: "Getting Started with koon"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with koon}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", eval = FALSE)
```

## Installation

koon requires a Rust toolchain (rustc >= 1.85). Install from source:

```{r}
# install.packages("remotes")
remotes::install_github("scrape-hub/koon", subdir = "crates/r")
```

## Your First Request

Create a client with a browser profile and make a GET request:

```{r}
library(koon)

client <- Koon$new("chrome")  # latest Chrome on Windows
resp <- client$get("https://httpbin.org/get")

resp$status   # 200
resp$version  # "h2"
resp$url      # final URL after redirects
```

## Response Structure

Every response is an R list. The most important components:

| Field          | Type       | Description                                          |
|----------------|------------|------------------------------------------------------|
| `status`       | integer    | HTTP status code (e.g. 200, 404)                     |
| `ok`           | logical    | TRUE when status is 2xx (success)                    |
| `version`      | character  | HTTP version: "HTTP/1.1", "h2" or "h3"               |
| `url`          | character  | Final URL after redirects                            |
| `body`         | raw        | Response body as raw bytes                           |
| `text`         | character  | Body decoded as text, `NULL` for binary bodies       |
| `content_type` | character  | Content-Type header, `NULL` if absent                |
| `headers`      | data.frame | Two columns: `name` and `value`                      |

`?Koon` lists all components.

```{r}
# Inspect response headers
resp$headers
#>              name                value
#> 1    content-type     application/json
#> 2  content-length                  523
#> ...
```

`text` is decoded with the charset of the Content-Type header. Binary
responses such as images have no text; use the raw `body`:

```{r}
img <- client$get("https://httpbin.org/image/png")
is.null(img$text)            # TRUE
writeBin(img$body, "image.png")
```

## POST Requests

Send data with `$post()`. The body is a string or a raw vector:

```{r}
# POST a text body
resp <- client$post("https://httpbin.org/post", "hello world")
cat(resp$text)

# POST JSON
resp <- client$post("https://httpbin.org/post", '{"name": "koon"}',
  headers = c("Content-Type" = "application/json"))

# POST binary data
resp <- client$post("https://httpbin.org/post", as.raw(c(0x01, 0x02, 0x03)))
```

## Parsing JSON Responses

Use `jsonlite` to parse JSON response bodies:

```{r}
library(jsonlite)

resp <- client$get("https://httpbin.org/get")
data <- fromJSON(resp$text)
data$headers$`User-Agent`
```

## Per-Request Headers

Override or add headers for a single request without changing the client:

```{r}
resp <- client$get("https://httpbin.org/headers",
  headers = c(Authorization = "Bearer my-token", "X-Custom" = "value"))
cat(resp$text)
```

## Other HTTP Methods

koon supports GET, POST, PUT, DELETE, PATCH and HEAD, and any other method
through `$request()`:

```{r}
client$put("https://httpbin.org/put", "data")
client$patch("https://httpbin.org/patch", "update")
client$delete("https://httpbin.org/delete")
client$head("https://httpbin.org/get")
client$request("OPTIONS", "https://httpbin.org/get")
```

## Browser Profiles

List the available profile names, one per profile (browser version and
OS):

```{r}
head(koon_browsers())
#> [1] "chrome131-windows" "chrome131-macos"   "chrome131-linux"
#> [4] "chrome131-android" "chrome132-windows" "chrome132-macos"
```

A name without a version selects the latest one, which keeps your code
current as koon adds new browser releases. Desktop profiles impersonate
Windows (Safari: macOS) unless you add an OS: `"chrome-macos"`,
`"firefox-linux"`, `"edge150-macos"`. Mobile profiles: `"chromemobile"`,
`"firefoxmobile"` (Android) and `"safarimobile"` (iOS).

Each profile reproduces the exact TLS, HTTP/2 and header fingerprint of that
browser version:

```{r}
# Firefox profile
ff <- Koon$new("firefox")
resp <- ff$get("https://tls.browserleaks.com/json")
cat(resp$text)  # shows JA3/JA4 fingerprint matching real Firefox

# Safari profile
safari <- Koon$new("safari")
resp <- safari$get("https://httpbin.org/get")
```
