---
title: "Getting Started with koon"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with koon}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", eval = FALSE)
```

## Installation

koon requires a Rust toolchain (rustc >= 1.85). Install from source:

```{r}
# install.packages("remotes")
remotes::install_github("nicescrape/koon", subdir = "crates/r")
```

## Your First Request

Create a client with a browser profile and make a GET request:

```{r}
library(koon)

client <- Koon$new("chrome145")
resp <- client$get("https://httpbin.org/get")

resp$status   # 200
resp$version  # "HTTP/2.0"
resp$url      # final URL after redirects
```

## Response Structure

Every response is an R list with these components:

| Field     | Type       | Description                            |
|-----------|------------|----------------------------------------|
| `status`  | integer    | HTTP status code (e.g. 200, 404)       |
| `ok`      | logical    | TRUE when status is 2xx (success)      |
| `version` | character  | HTTP version (e.g. "HTTP/2.0")         |
| `url`     | character  | Final URL after redirects              |
| `body`    | raw        | Response body as raw bytes             |
| `text`    | character  | Response body as UTF-8 string          |
| `headers` | data.frame | Two columns: `name` and `value`        |

```{r}
# Inspect response headers
resp$headers
#>              name                value
#> 1    content-type application/json
#> 2 content-length                523
#> ...
```

## POST Requests

Send data with `$post()`. The body must be a raw vector:

```{r}
# POST with a text body
resp <- client$post("https://httpbin.org/post", charToRaw("hello world"))
cat(resp$text)

# POST JSON
json_body <- '{"name": "koon", "version": "0.4.5"}'
resp <- client$post("https://httpbin.org/post", charToRaw(json_body))
```

## Parsing JSON Responses

Use `jsonlite` to parse JSON response bodies:

```{r}
library(jsonlite)

resp <- client$get("https://httpbin.org/get")
data <- fromJSON(resp$text)
data$headers$`User-Agent`
```

## Per-Request Headers

Override or add headers for a single request without changing the client:

```{r}
resp <- client$get("https://httpbin.org/headers",
  headers = c(Authorization = "Bearer my-token", "X-Custom" = "value"))
cat(resp$text)
```

## Other HTTP Methods

koon supports GET, POST, PUT, DELETE, PATCH, and HEAD:

```{r}
client$put("https://httpbin.org/put", charToRaw("data"))
client$patch("https://httpbin.org/patch", charToRaw("update"))
client$delete("https://httpbin.org/delete")
client$head("https://httpbin.org/get")
```

## Browser Profiles

koon ships with 50+ browser profiles. List them all:

```{r}
koon_browsers()
#>  [1] "chrome131" "chrome132" ... "chrome145"
#> [16] "firefox135" ... "firefox147"
#> [29] "safari156" "safari160" "safari170" "safari180" "safari183"
#> [34] "edge131" ... "edge145"
#> [49] "opera124" ... "opera127"
```

Each profile reproduces the exact TLS, HTTP/2, and header fingerprint of that browser version:

```{r}
# Firefox profile
ff <- Koon$new("firefox147")
resp <- ff$get("https://tls.browserleaks.com/json")
cat(resp$text)  # shows JA3/JA4 fingerprint matching real Firefox

# Safari profile
safari <- Koon$new("safari183")
resp <- safari$get("https://httpbin.org/get")
```
