---
title: "Sessions and Cookies"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Sessions and Cookies}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", eval = FALSE)
```

## Cookie Persistence

Cookies are automatically stored and sent with subsequent requests:

```{r}
library(koon)

client <- Koon$new("chrome145")

# Set a cookie
client$get("https://httpbin.org/cookies/set/session_id/abc123")

# Cookie is included in the next request
resp <- client$get("https://httpbin.org/cookies")
cat(resp$text)
#> {"cookies": {"session_id": "abc123"}}
```

Multiple cookies work the same way:

```{r}
client$get("https://httpbin.org/cookies/set/user/alice")
client$get("https://httpbin.org/cookies/set/lang/en")

resp <- client$get("https://httpbin.org/cookies")
jsonlite::fromJSON(resp$text)$cookies
#> $session_id
#> [1] "abc123"
#> $user
#> [1] "alice"
#> $lang
#> [1] "en"
```

## Saving and Loading Sessions

Save the entire session state (cookies + TLS session tickets) to a JSON string, then restore it later:

```{r}
# Save session to a variable
session_json <- client$save_session()

# Save to file for persistence across R sessions
writeLines(session_json, "my_session.json")

# Later: create a new client and restore the session
client2 <- Koon$new("chrome145")
client2$load_session(readLines("my_session.json", warn = FALSE))

# Cookies are restored
resp <- client2$get("https://httpbin.org/cookies")
cat(resp$text)
```

## Use Case: Login Session

A typical workflow for sites that require authentication:

```{r}
client <- Koon$new("chrome145")

# Step 1: POST login credentials
login_body <- '{"username": "user", "password": "pass"}'
resp <- client$post("https://example.com/api/login", charToRaw(login_body))

# Step 2: Session cookies are now stored — subsequent requests are authenticated
resp <- client$get("https://example.com/api/profile")
profile <- jsonlite::fromJSON(resp$text)

# Step 3: Save session so you don't have to login again
writeLines(client$save_session(), "session.json")
```

Restore the session in a later script:

```{r}
client <- Koon$new("chrome145")
client$load_session(readLines("session.json", warn = FALSE))

# Authenticated request without re-login
resp <- client$get("https://example.com/api/profile")
```

## Exporting the Browser Profile

Export the full browser profile (TLS config, HTTP/2 settings, headers) as JSON:

```{r}
client <- Koon$new("safari183")
profile_json <- client$export_profile()
cat(substr(profile_json, 1, 200))  # preview first 200 chars
writeLines(profile_json, "safari183_profile.json")
```

This is useful for debugging fingerprint issues or sharing configurations.
